maxent model avec xvalidation (year-based test training)

### 2019-04-16 src/maxent_avec_xvalidation.Rmd
playing with aic for paper 2... doesnt work (cant loop through the folds)

    #test auc scores and other lovely things you might want to include
    ev <- evaluate(p = testp, a= testb, model = mod)
    evauc <- ev@auc
    evcor <- ev@cor
    evpcor <- ev@pcor
    evnp <- ev@np
    evna <- ev@na
    evmaxtprtnr <- threshold(ev, 'spec_sens')
    evmaxkap <- threshold(ev, 'kappa')
    evno_omission <- threshold(ev, 'no_omission')
    evprevalence <- threshold(ev, 'prevalence')
    evequal_sens_spec <- threshold(ev, 'equal_sens_spec')

    #calculate minimal predicted area using ecospat
    aicect$mpa <- ecospat.mpa(samplepred$Cumulative.prediction, perc = 0.9) #90%

    for (i in 1:nrow(aicetc)){
      if(aicetc$regularization[i] == betamval){
      aicetc$Train.AUC[i] <- trainauc
      aicetc$n[i] <- notrainingpoints
      aicetc$coefficients[i] <- nocoeff
      aicetc$sum.of.logs[i] <- sumsamplepred
      aicetc$Test.AUC[i] <- evauc
      aicetc$evcor[i] <- evcor
      aicetc$evpcor[i] <- evpcor
      aicetc$nopresence[i] <- evnp
      aicetc$nobackground[i] <- evna
      aicetc$maxsumsenspec[i] <- evmaxtprtnr
      aicetc$maxsumsenspec[i] <- evmaxkap
      aicetc$no_omission[i] <- evno_omission
      aicetc$equal_sens_spec[i] <- evequal_sens_spec
      aicetc$bic[i] <- bic #not sure this is correct...
      }
    }
  }

@@

    #test auc scores and other lovely things you might want to include
    ev <- evaluate(p = testp, a= testb, model = mod)
    evauc <- ev@auc
    evcor <- ev@cor
    evpcor <- ev@pcor
    evnp <- ev@np
    evna <- ev@na
    evmaxtprtnr <- threshold(ev, 'spec_sens')
    evmaxkap <- threshold(ev, 'kappa')
    evno_omission <- threshold(ev, 'no_omission')
    evprevalence <- threshold(ev, 'prevalence')
    evequal_sens_spec <- threshold(ev, 'equal_sens_spec')

      aicetc$Train.AUC <- trainauc
      aicetc$n <- notrainingpoints
      aicetc$coefficients <- nocoeff
      aicetc$sum.of.logs <- sumsamplepred
      aicetc$Test.AUC <- evauc
      aicetc$evcor <- evcor
      aicetc$evpcor <- evpcor
      aicetc$nopresence <- evnp
      aicetc$nobackground <- evna
      aicetc$maxsumsenspec <- evmaxtprtnr
      aicetc$maxkap <- evmaxkap
      aicetc$no_omission <- evno_omission
      aicetc$prevalence <- evprevalence
      aicetc$equal_sens_spec <- evequal_sens_spec
      aicetc$bic <- bic #not sure this is correct...
      aicetc$beta <- betaval

@@

    #calculate minimal predicted area using ecospat
    aicetc$mpa <- ecospat.mpa(samplepred$Cumulative.prediction, perc = 0.9) #90%

@@

    for (td in 1:nrow(unlayer_yr)){
      temp_depth <- raster(unlayer_yr$temp_depth[td])
      crs(temp_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(temp_depth) <- "temp_depth"
      temp_depth <- projectRaster(temp_depth, aea)
      chl_surface <- raster(unlayer_yr$chl_surface[td])
      crs(chl_surface) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(chl_surface) <- "chl_surface"
      chl_surface <- projectRaster(chl_surface, aea)
      o2_depth <- raster(unlayer_yr$o2_depth[td])
      crs(o2_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(o2_depth) <- "o2_depth"
      o2_depth <- projectRaster(o2_depth, aea)
      salinity_depth <- raster(unlayer_yr$salinity_depth[td])
      crs(salinity_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(salinity_depth) <- "salinity_depth"
      salinity_depth <- projectRaster(salinity_depth, aea)
      nao_sample <- raster(unlayer_yr$nao_sample[td])
      crs(nao_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(nao_sample) <- "nao_sample"
      nao_sample <- projectRaster(nao_sample, aea)
      nao_prev <- raster(unlayer_yr$nao_prev[td])
      crs(nao_prev) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(nao_prev) <- "nao_prev"
      nao_prev <- projectRaster(nao_prev, aea)
      nao_winter <- raster(unlayer_yr$nao_winter[td])
      crs(nao_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
      names(nao_winter) <- "nao_winter"
      nao_winter <- projectRaster(nao_winter, aea)
      amo_sample <- raster(unlayer_yr$amo_sample[td])
      crs(amo_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(amo_sample) <- "amo_sample"
      amo_sample <- projectRaster(amo_sample, aea)
      amo_winter <- raster(unlayer_yr$amo_winter[td])
      crs(amo_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
      names(amo_winter) <- "amo_winter"
      amo_winter <- projectRaster(amo_winter, aea)
      stackn <- unlayer_yr$stackname[td]
      stack <- stack(temp_depth, salinity_depth, o2_depth, chl_surface, nao_sample, nao_prev, nao_winter, amo_sample, amo_winter)
      #stackSave(test,unlayer_yr$stackname[td])
     # pred <- predict(mod, stack, file = paste0("../output/maxent/predictions/", mthna, "/", stackn, ".asc"), overwrite=TRUE, args='outputformat=cloglog') 
      predcum <- predict(mod, stack, file = paste0("../output/maxent/predictions/", mthna, "/", stackn, ".asc"), overwrite=TRUE, args='outputformat=cumulative') 
     # prplot <- plot(pred, png(paste0("../output/maxent/predictions/", mthna, "/", stackn, ".png"))) 
      prplotcum <- plot(predcum, png(paste0("../output/maxent/predictions/", mthna, "/", stackn, ".png"))) 
      dev.off() # stops automatic saving of the plot to a png
    }
}

@@

```{r avg asc layers}
asc_list <- list.files(paste0("../output/maxent/predictions/", mthna), pattern = "*.asc", full.names = TRUE)
depthlayers <- data.frame(cbind(unique(stdep$ascdepths)))
names(depthlayers)[names(depthlayers) == "cbind.unique.stdep.ascdepths.."] <- "depth"
depthlayers$depth <- as.character(depthlayers$depth)

@@

for (d in 1:nrow(depthlayers)){
  dep <- depthlayers$depth[d]
  for (a in 1:length(asc_list)){
    asc <- asc_list[a]
    if (grepl(dep, asc)){
      depthlayers[d , paste0("a", colno)] <- asc
        colno <- colno+1
    }
  }
}
write.csv(depthlayers, (paste0("../output/maxent/predictions/", mthna, "/asclayerbydepth.csv")), row.names = TRUE)

@@

asc120  <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_120.asc"))
asc41.18 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_41.18.asc"))
asc1.55586 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_1.55586.asc"))
asc1045.85 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_1045.85.asc"))
asc108.03 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_108.03.asc"))
asc11.7737 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_11.7737.asc"))
asc1151.99 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_1151.99.asc"))
asc1265.86 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_1265.86.asc"))
asc13.991 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_13.991.asc"))
asc133.076 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_133.076.asc"))
asc1387.38 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_1387.38.asc"))
asc147.406 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_147.406.asc"))
asc16.5253 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_16.5253.asc"))
asc163.165 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_163.165.asc"))
asc180.55 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_180.55.asc"))
asc19.4298 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_19.4298.asc"))
asc199.79 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_199.79.asc"))
asc2.66768 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_2.66768.asc"))
asc22.7576 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_22.7576.asc"))
asc221.141 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_221.141.asc"))
asc244.891 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_244.891.asc"))
asc26.5583 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_26.5583.asc"))
asc271.356 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_271.356.asc"))
asc3.85628 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_3.85628.asc"))
asc30.8746 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_30.8746.asc"))
asc300.888 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_300.888.asc"))
asc333.863 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_333.863.asc"))
asc35.7402 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_35.7402.asc"))
asc370.689 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_370.689.asc"))
asc411.794 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_411.794.asc"))
asc457.626 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_457.626.asc"))
asc47.2119 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_47.2119.asc"))
asc5.14036 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_5.14036.asc"))
asc508.64 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_508.64.asc"))
asc53.8506 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_53.8506.asc"))
asc565.292 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_565.292.asc"))
asc6.54303 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_6.54303.asc"))
asc61.1128 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_61.1128.asc"))
asc628.026 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_628.026.asc"))
asc69.0217 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_69.0217.asc"))
asc697.259 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_697.259.asc"))
asc77.6112 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_77.6112.asc"))
asc773.368 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_773.368.asc"))
asc8.09252 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_8.09252.asc"))
asc856.679 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_856.679.asc"))
asc86.9294 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_86.9294.asc"))
asc9.82275 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_9.82275.asc"))
asc947.448 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_947.448.asc"))
asc97.0413 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_97.0413.asc"))

stackavg <- stack(asc120, asc41.18, asc1.55586, asc1045.85, asc108.03, asc11.7737, asc1151.99, asc1265.86, asc13.991, asc133.076, asc1387.38, asc147.406, asc16.5253, asc163.165, asc180.55, asc19.4298, asc199.79, asc2.66768, asc22.7576, asc221.141, asc244.891, asc26.5583, asc271.356, asc3.85628, asc30.8746, asc300.888, asc333.863, asc35.7402, asc370.689, asc411.794, asc457.626, asc47.2119, asc5.14036, asc508.64, asc53.8506, asc565.292, asc6.54303, asc61.1128, asc628.026, asc69.0217, asc697.259, asc77.6112, asc773.368, asc8.09252, asc856.679, asc86.9294, asc9.82275, asc947.448, asc97.0413)

stsum <- sum(stackavg, na.rm = TRUE)
  writeRaster(stsum, (paste0("../output/maxent/predictions/", mthna, "/sum_", mthna, ".asc")), overwrite=TRUE)
  sumplot <- plot(stsum, png(paste0("../output/maxent/predictions/", mthna, "/sum_", mthna, ".png"))) 
  dev.off()
stavg <- calc(stackavg, fun = mean, na.rm = TRUE)
  writeRaster(stavg, (paste0("../output/maxent/predictions/", mthna, "/avg_", mthna, ".asc")), overwrite=TRUE)
  avgplot <- plot(stavg, png(paste0("../output/maxent/predictions/", mthna, "/avg_", mthna, ".png"))) 
  dev.off()

>>>>

   #test auc scores and other lovely things you might want to include
    ev <- evaluate(p = testp, a= testb, model = mod)
    evauc <- ev@auc
    evcor <- ev@cor
    evpcor <- ev@pcor
    evnp <- ev@np
    evna <- ev@na
    evmaxtprtnr <- threshold(ev, 'spec_sens')
    evmaxkap <- threshold(ev, 'kappa')
    evno_omission <- threshold(ev, 'no_omission')
    evprevalence <- threshold(ev, 'prevalence')
    evequal_sens_spec <- threshold(ev, 'equal_sens_spec')
    evsensitivity <- threshold(ev, 'sensitivity')

      aicetc$train_AUC <- trainauc
      aicetc$no_trainng_points <- notrainingpoints
      aicetc$test_coefficients <- nocoeff
      aicetc$test_sum.of.logs <- sumsamplepred
      aicetc$test_AUC <- evauc
      aicetc$test_evcor <- evcor
      aicetc$test_evpcor <- evpcor
      aicetc$test_nopresence <- evnp
      aicetc$test_nobackground <- evna
      aicetc$test_maxsumsenspec <- evmaxtprtnr
      aicetc$test_maxkap <- evmaxkap
      aicetc$test_no_omission <- evno_omission
      aicetc$test_prevalence <- evprevalence
      aicetc$test_equal_sens_spec <- evequal_sens_spec
      aicetc$test_sensitivity <- evsensitivity
      aicetc$test_bic <- bic #not sure this is correct...
      aicetc$beta <- betaval

    #calculate minimal predicted area using ecospat
    aicetc$mpa_0.9_cum <- ecospat.mpa(samplepred$Cumulative.prediction, perc = 0.9) #90%
      }
    }

@@

    #test auc scores and other lovely things you might want to include
    ev <- evaluate(p = testp, a= testb, model = mod)
    evauc <- ev@auc
    evcor <- ev@cor
    evpcor <- ev@pcor
    evnp <- ev@np
    evna <- ev@na
    evmaxtprtnr <- threshold(ev, 'spec_sens')
    evmaxkap <- threshold(ev, 'kappa')
    evno_omission <- threshold(ev, 'no_omission')
    evprevalence <- threshold(ev, 'prevalence')
    evequal_sens_spec <- threshold(ev, 'equal_sens_spec')
    evsensitivity <- threshold(ev, 'sensitivity')

      aicetc$train_AUC <- trainauc
      aicetc$no_trainng_points <- notrainingpoints
      aicetc$test_coefficients <- nocoeff
      aicetc$test_sum.of.logs <- sumsamplepred
      aicetc$test_AUC <- evauc
      aicetc$test_evcor <- evcor
      aicetc$test_evpcor <- evpcor
      aicetc$test_nopresence <- evnp
      aicetc$test_nobackground <- evna
      aicetc$test_maxsumsenspec <- evmaxtprtnr
      aicetc$test_maxkap <- evmaxkap
      aicetc$test_no_omission <- evno_omission
      aicetc$test_prevalence <- evprevalence
      aicetc$test_equal_sens_spec <- evequal_sens_spec
      aicetc$test_sensitivity <- evsensitivity
      aicetc$test_bic <- bic #not sure this is correct...
      aicetc$beta <- betaval

@@

    #calculate minimal predicted area using ecospat
    aicetc$mpa_0.9_cum <- ecospat.mpa(samplepred$Cumulative.prediction, perc = 0.9) #90%

@@

    for (td in 1:nrow(unlayer_yr)){
      temp_depth <- raster(unlayer_yr$temp_depth[td])
      crs(temp_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(temp_depth) <- "temp_depth"
      temp_depth <- projectRaster(temp_depth, aea)
      chl_surface <- raster(unlayer_yr$chl_surface[td])
      crs(chl_surface) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(chl_surface) <- "chl_surface"
      chl_surface <- projectRaster(chl_surface, aea)
      o2_depth <- raster(unlayer_yr$o2_depth[td])
      crs(o2_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(o2_depth) <- "o2_depth"
      o2_depth <- projectRaster(o2_depth, aea)
      salinity_depth <- raster(unlayer_yr$salinity_depth[td])
      crs(salinity_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(salinity_depth) <- "salinity_depth"
      salinity_depth <- projectRaster(salinity_depth, aea)
      nao_sample <- raster(unlayer_yr$nao_sample[td])
      crs(nao_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(nao_sample) <- "nao_sample"
      nao_sample <- projectRaster(nao_sample, aea)
      nao_prev <- raster(unlayer_yr$nao_prev[td])
      crs(nao_prev) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(nao_prev) <- "nao_prev"
      nao_prev <- projectRaster(nao_prev, aea)
      nao_winter <- raster(unlayer_yr$nao_winter[td])
      crs(nao_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
      names(nao_winter) <- "nao_winter"
      nao_winter <- projectRaster(nao_winter, aea)
      amo_sample <- raster(unlayer_yr$amo_sample[td])
      crs(amo_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(amo_sample) <- "amo_sample"
      amo_sample <- projectRaster(amo_sample, aea)
      amo_winter <- raster(unlayer_yr$amo_winter[td])
      crs(amo_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
      names(amo_winter) <- "amo_winter"
      amo_winter <- projectRaster(amo_winter, aea)
      stackn <- unlayer_yr$stackname[td]
      stack <- stack(temp_depth, salinity_depth, o2_depth, chl_surface, nao_sample, nao_prev, nao_winter, amo_sample, amo_winter)
      #stackSave(test,unlayer_yr$stackname[td])
      pred <- predict(mod, stack, file = paste0("../output/maxent/predictions/", mthna, "/", "cloglog_", stackn, ".asc"), overwrite=TRUE, args='outputformat=cloglog') 
      predcum <- predict(mod, stack, file = paste0("../output/maxent/predictions/", mthna, "/", "cumu_", stackn, ".asc"), overwrite=TRUE, args=c('outputformat=Cumulative')) 
      prplot <- plot(pred, png(paste0("../output/maxent/predictions/", mthna, "/", "cloglog_", stackn, ".png")))
      dev.off() # stops automatic saving of the plot to a png
      prplotcum <- plot(predcum, png(paste0("../output/maxent/predictions/", mthna, "/", "cumu_", stackn, ".png"))) 
      dev.off() # stops automatic saving of the plot to a png
    }
}

@@

```{r avg asc layers cloglog}
asc_list <- list.files(paste0("../output/maxent/predictions/", mthna), pattern = "cloglog*.asc", full.names = TRUE)
depthlayers <- data.frame(cbind(unique(stdep$ascdepths)))
names(depthlayers)[names(depthlayers) == "cbind.unique.stdep.ascdepths.."] <- "depth"
depthlayers$depth <- as.character(depthlayers$depth)

@@

for (d in 1:nrow(depthlayers)){
  dep <- depthlayers$depth[d]
  for (a in 1:length(asc_list)){
    asc <- asc_list[a]
    if (grepl(dep, asc)){
      depthlayers[d , paste0("a", colno)] <- asc
        colno <- colno+1
    }
  }
}
write.csv(depthlayers, (paste0("../output/maxent/predictions/", mthna, "/cloglog_asclayerbydepth.csv")), row.names = TRUE)

@@

clog_asc120  <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_120.asc"))
clog_asc41.18 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_41.18.asc"))
clog_asc1.55586 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_1.55586.asc"))
clog_asc1045.85 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_1045.85.asc"))
clog_asc108.03 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_108.03.asc"))
clog_asc11.7737 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_11.7737.asc"))
clog_asc1151.99 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_1151.99.asc"))
clog_asc1265.86 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_1265.86.asc"))
clog_asc13.991 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_13.991.asc"))
clog_asc133.076 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_133.076.asc"))
clog_asc1387.38 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_1387.38.asc"))
clog_asc147.406 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_147.406.asc"))
clog_asc16.5253 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_16.5253.asc"))
clog_asc163.165 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_163.165.asc"))
clog_asc180.55 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_180.55.asc"))
clog_asc19.4298 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_19.4298.asc"))
clog_asc199.79 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_199.79.asc"))
clog_asc2.66768 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_2.66768.asc"))
clog_asc22.7576 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_22.7576.asc"))
clog_asc221.141 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_221.141.asc"))
clog_asc244.891 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_244.891.asc"))
clog_asc26.5583 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_26.5583.asc"))
clog_asc271.356 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_271.356.asc"))
clog_asc3.85628 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_3.85628.asc"))
clog_asc30.8746 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_30.8746.asc"))
clog_asc300.888 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_300.888.asc"))
clog_asc333.863 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_333.863.asc"))
clog_asc35.7402 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_35.7402.asc"))
clog_asc370.689 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_370.689.asc"))
clog_asc411.794 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_411.794.asc"))
clog_asc457.626 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_457.626.asc"))
clog_asc47.2119 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_47.2119.asc"))
clog_asc5.14036 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_5.14036.asc"))
clog_asc508.64 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_508.64.asc"))
clog_asc53.8506 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_53.8506.asc"))
clog_asc565.292 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_565.292.asc"))
clog_asc6.54303 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_6.54303.asc"))
clog_asc61.1128 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_61.1128.asc"))
clog_asc628.026 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_628.026.asc"))
clog_asc69.0217 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_69.0217.asc"))
clog_asc697.259 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_697.259.asc"))
clog_asc77.6112 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_77.6112.asc"))
clog_asc773.368 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_773.368.asc"))
clog_asc8.09252 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_8.09252.asc"))
clog_asc856.679 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_856.679.asc"))
clog_asc86.9294 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_86.9294.asc"))
clog_asc9.82275 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_9.82275.asc"))
clog_asc947.448 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_947.448.asc"))
clog_asc97.0413 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_97.0413.asc"))

stackavg <- stack(clog_asc120, clog_asc41.18, clog_asc1.55586, clog_asc1045.85, clog_asc108.03, clog_asc11.7737, clog_asc1151.99, clog_asc1265.86, clog_asc13.991, clog_asc133.076, clog_asc1387.38, clog_asc147.406, clog_asc16.5253, clog_asc163.165, clog_asc180.55, clog_asc19.4298, clog_asc199.79, clog_asc2.66768, clog_asc22.7576, clog_asc221.141, clog_asc244.891, clog_asc26.5583, clog_asc271.356, clog_asc3.85628, clog_asc30.8746, clog_asc300.888, clog_asc333.863, clog_asc35.7402, clog_asc370.689, clog_asc411.794, clog_asc457.626, clog_asc47.2119, clog_asc5.14036, clog_asc508.64, clog_asc53.8506, clog_asc565.292, clog_asc6.54303, clog_asc61.1128, clog_asc628.026, clog_asc69.0217, clog_asc697.259, clog_asc77.6112, clog_asc773.368, clog_asc8.09252, clog_asc856.679, clog_asc86.9294, clog_asc9.82275, clog_asc947.448, clog_asc97.0413)

stsum <- sum(stackavg, na.rm = TRUE)
  writeRaster(stsum, (paste0("../output/maxent/predictions/", mthna, "/clog_sum_", mthna, ".asc")), overwrite=TRUE)
  sumplot <- plot(stsum, png(paste0("../output/maxent/predictions/", mthna, "/clog_sum_", mthna, ".png"))) 
  dev.off()
stavg <- calc(stackavg, fun = mean, na.rm = TRUE)
  writeRaster(stavg, (paste0("../output/maxent/predictions/", mthna, "/clog_avg_", mthna, ".asc")), overwrite=TRUE)
  avgplot <- plot(stavg, png(paste0("../output/maxent/predictions/", mthna, "/clog_avg_", mthna, ".png"))) 
  dev.off()
